\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{bm}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{listings}
\usepackage{url}
\usepackage{cite}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\definecolor{cmuRed}{RGB}{196,18,48}
\definecolor{codeGray}{RGB}{96,96,96}

\lstdefinestyle{ccode}{
    language=C,
    basicstyle=\ttfamily\footnotesize,
    keywordstyle=\color{cmuRed}\bfseries,
    commentstyle=\color{codeGray}\itshape,
    stringstyle=\color{codeGray},
    numbers=left,
    numberstyle=\tiny\color{codeGray},
    frame=single,
    framerule=0.4pt,
    breaklines=true,
    showstringspaces=false,
    captionpos=b,
}

\begin{document}

\title{A Structure-Exploiting C ADMM Solver for Embedded Quadrotor MPC,\\
with Solver Benchmarks and Neural Distillation}

\author{\IEEEauthorblockN{Vrishabh Kenkre}
\IEEEauthorblockA{\textit{Department of Mechanical Engineering} \\
\textit{Carnegie Mellon University}\\
Pittsburgh, PA, USA \\
vkenkre@andrew.cmu.edu}
}

\maketitle

\begin{abstract}
We implement a hand-rolled, structure-exploiting ADMM solver in C for linear MPC of a Bitcraze Crazyflie 2 quadrotor and benchmark it against OSQP and the GPU-accelerated ReLU-QP solver. The custom ADMM caches a Riccati recursion in the infinite-horizon LQR backward pass and reduces the active per-iteration work to $12\!\times\!12$ block operations rather than a sparse Cholesky on the full $332\!\times\!332$ KKT system. On a figure-8 trajectory at $1.11$~m/s the controller achieves $3.42$~mm steady-state RMSE with median solve time of $9.4~\mu$s on a single laptop CPU core, $22\times$ faster than tuned OSQP at slightly better accuracy. ReLU-QP, a recent general-purpose ADMM solver that unrolls each iteration as a GPU-parallel neural network forward pass, converges reliably to $4.85$~mm tracking RMSE on the same task in $1.84$~ms median solve time on an NVIDIA L40S GPU. At batch size $1$ on this $80$-variable QP, ReLU-QP's solve time is dominated by kernel launch and CPU$\leftrightarrow$GPU transfer overhead rather than compute --- $196\times$ slower than our C ADMM. We use this finding to characterize the regime boundary between specialized CPU solvers and batched GPU solvers: ReLU-QP's advantage activates at large batch sizes (multi-agent fleets, Monte-Carlo trajectory sampling), not at the single-problem onboard latency regime that linear quadrotor MPC occupies. Finally, we distill the MPC controller into a $6{,}276$-parameter feedforward network using DAgger with DART noise injection. The distilled policy tracks figure-8 at $4.1$~mm RMSE ($\sim 20\%$ degradation versus the teacher) while running in $2.1~\mu$s of pure C inference --- a $\sim 4.5\times$ speedup over the tuned C ADMM that eliminates the dynamics model and solver from the deployment binary.
\end{abstract}

\begin{IEEEkeywords}
quadrotor, model predictive control, ADMM, embedded optimization, policy distillation, DAgger
\end{IEEEkeywords}

\section{Introduction}

Model predictive control (MPC) is the dominant approach to constrained quadrotor trajectory tracking, but its real-time viability on small platforms is limited by the cost of solving a quadratic program (QP) every control step. The Bitcraze Crazyflie 2 has $192$~KB of SRAM and a $168$~MHz Cortex-M4; off-the-shelf solvers like OSQP~\cite{stellato2020osqp} are general-purpose and use sparse Cholesky factorizations that are not well matched to the dense, low-dimensional structure of a $20$-step linear MPC problem.

Two recent solver developments target this regime from opposite directions. TinyMPC~\cite{nguyen2024tinympc} exploits the Riccati structure of the infinite-horizon LQR feedback law to reduce per-iteration work to $n_x \times n_x$ block operations, where $n_x = 12$ for a quadrotor. ReLU-QP~\cite{bishop2024reluqp} reformulates ADMM as a fixed-architecture neural network whose forward pass executes on a GPU at the rate of a few hundred microseconds per batched solve --- attractive for parallel evaluation across many trajectories or many robots, but designed for medium-to-large state dimensions ($n \gtrsim 100$).

This paper presents a from-scratch C implementation of the TinyMPC-style solver tuned for the Crazyflie, an empirical comparison against OSQP and ReLU-QP, and a downstream policy distillation step that compresses the entire MPC pipeline into a small feedforward network. The contributions are:

\begin{enumerate}
    \item A complete, MIT-licensed C ADMM solver with cached Riccati recursion, $9.4~\mu$s median solve time on commodity laptop CPU at $3.42$~mm closed-loop tracking RMSE, and verified zero linearization error against CasADi autodiff.
    \item A head-to-head benchmark against OSQP and ReLU-QP, with empirical regime characterization showing the boundary between structure-exploiting and parallelism-exploiting QP solvers for embedded MPC.
    \item A DAgger~\cite{ross2011dagger}-with-DART~\cite{laskey2017dart} distillation of the MPC controller into a $6$K-parameter network exported to C, with $2.1~\mu$s deployment latency and $4.1$~mm tracking RMSE.
\end{enumerate}

The full code, trained policy weights, and replication instructions are available at the repository accompanying this paper.

\section{System Model and MPC Formulation}

\subsection{Quadrotor Dynamics}

We use the standard $12$-state Crazyflie model: $\bm{x} = [\bm{p}^\top, \bm{v}^\top, \bm{\eta}^\top, \bm{\omega}^\top]^\top$ where $\bm{p}, \bm{v} \in \mathbb{R}^3$ are inertial position and velocity, $\bm{\eta} = (\phi, \theta, \psi)$ are roll-pitch-yaw, and $\bm{\omega} \in \mathbb{R}^3$ is the body-frame angular velocity. The control input is $\bm{u} = [T, \tau_x, \tau_y, \tau_z]^\top$ with collective thrust $T$ and three body torques. We use the MuJoCo Menagerie Crazyflie~2 model after applying the following corrections, which are required to obtain physically meaningful dynamics:

\begin{itemize}
    \item Thrust range corrected from the default $[0, 0.0155]$ to the manufacturer-rated $[0, 0.6]$~N total thrust.
    \item Torque gear magnitudes adjusted so that maximum yaw torque is approximately $0.0069$~N$\cdot$m.
    \item Gear sign on $\tau_z$ inverted to match the sense convention used in the dynamics derivation.
\end{itemize}

We linearize about hover ($\bm{x}_\text{hover} = \bm{0}$, $T_\text{hover} = mg$) to obtain $\dot{\bm{x}} = A\bm{x} + B\bm{u} + \bm{d}$ where $\bm{d}$ absorbs gravity and the hover thrust offset. Discretization at $\Delta t = 10$~ms by zero-order hold yields $A_d, B_d, \bm{d}_\text{ctrl}$ matrices used by the MPC. We verified the linearization against a CasADi autodiff of the nonlinear MuJoCo dynamics at the equilibrium and obtained Frobenius-norm error $\|A_\text{analytic} - A_\text{casadi}\|_F = 0$.

\subsection{Linear MPC}

The MPC problem is
\begin{equation}
\begin{aligned}
\min_{\bm{x}, \bm{u}} \quad & \sum_{k=0}^{N-1} \tfrac{1}{2}(\bm{x}_k - \bm{x}_k^\text{ref})^\top Q (\bm{x}_k - \bm{x}_k^\text{ref}) + \tfrac{1}{2}\bm{u}_k^\top R \bm{u}_k \\
& \quad + \tfrac{1}{2}(\bm{x}_N - \bm{x}_N^\text{ref})^\top Q_f (\bm{x}_N - \bm{x}_N^\text{ref}) \\
\text{s.t.} \quad & \bm{x}_{k+1} = A_d \bm{x}_k + B_d \bm{u}_k + \bm{d}_\text{ctrl} \\
& \bm{u}_\text{min} \le \bm{u}_k \le \bm{u}_\text{max} \\
& \bm{x}_0 = \bm{x}(t)
\end{aligned}
\label{eq:mpc}
\end{equation}
with horizon $N = 20$, $Q = \text{diag}(Q_p, Q_v, Q_\eta, Q_\omega)$, and a control penalty $R$ in which the thrust weight ($30$) and torque weights ($1500$) differ by a factor of $50$, reflecting the physical difference between collective-thrust authority and individual-rotor torque authority on the Crazyflie.

\section{Custom ADMM Solver in C}
\label{sec:admm}

\subsection{Splitting and Algorithm}

We apply ADMM to (\ref{eq:mpc}) by splitting the input variable $\bm{u}$ from a slack variable $\bm{z}$ that absorbs the box constraint:
\begin{equation}
\begin{aligned}
\min_{\bm{u}, \bm{z}} \quad & f(\bm{u}) + g(\bm{z}) \\
\text{s.t.} \quad & \bm{u} = \bm{z}
\end{aligned}
\end{equation}
where $f$ is the quadratic objective with the dynamics substituted in (closed form), and $g$ is the indicator function of the box $[\bm{u}_\text{min}, \bm{u}_\text{max}]$. The augmented Lagrangian is
\begin{equation}
L_\rho(\bm{u}, \bm{z}, \bm{y}) = f(\bm{u}) + g(\bm{z}) + \bm{y}^\top(\bm{u} - \bm{z}) + \tfrac{\rho}{2}\|\bm{u} - \bm{z}\|^2
\end{equation}
and the iteration is the canonical three-step update~\cite{boyd2011admm}:
\begin{align}
\bm{u}^{k+1} &= -K_\infty \bm{x} - \bm{d}_\text{ctrl} + (\rho/\sigma)(\bm{z}^k - \bm{y}^k) \label{eq:admm_u} \\
\bm{z}^{k+1} &= \Pi_{[\bm{u}_\text{min}, \bm{u}_\text{max}]}(\bm{u}^{k+1} + \bm{y}^k / \rho) \label{eq:admm_z} \\
\bm{y}^{k+1} &= \bm{y}^k + \rho(\bm{u}^{k+1} - \bm{z}^{k+1}) \label{eq:admm_y}
\end{align}
where $K_\infty$ is the infinite-horizon LQR gain solving the discrete algebraic Riccati equation (DARE) for $(A_d, B_d, Q, R + \sigma I)$, and $\sigma > 0$ is a small regularizer.

\subsection{The Riccati Caching Trick}

The expensive step in a generic ADMM solver is~\eqref{eq:admm_u}, which requires solving an $n \times n$ linear system. OSQP, for example, factorizes the full sparse KKT system, which for our problem ($N = 20$, $n_x = 12$, $n_u = 4$) has $332$ variables.

Following TinyMPC~\cite{nguyen2024tinympc}, we observe that for an MPC problem the optimal $\bm{u}^*$ at iteration $k+1$ is a linear function of the current state and a low-rank correction term $\rho(\bm{z}^k - \bm{y}^k)$. The correction propagates backward through the horizon via a Riccati-style recursion that involves only $n_x \times n_x$ block operations. We pre-compute and cache the steady-state gain $K_\infty$ and the propagation matrices $C_1, C_2$ once at startup; the per-iteration work in (\ref{eq:admm_u}) is then a single matrix-vector product on $12 \times 12$ blocks.

This reduces the cost of (\ref{eq:admm_u}) from $\mathcal{O}((N(n_x + n_u))^3)$ for sparse Cholesky to $\mathcal{O}(N \cdot n_x^2)$ for the cached recursion --- approximately $22{,}000$ FLOPs per iteration in our implementation versus $2.25 \times 10^6$ FLOPs for the equivalent OSQP factorization.

\subsection{Implementation Details}

The C implementation is approximately $400$ lines and uses no dynamic allocation. The hot loop is shown in Listing~\ref{lst:admm}. We use stack-allocated static arrays sized to a maximum problem dimension chosen at compile time, and a zero-overhead Python binding via \texttt{ctypes} for the offline benchmarking and DAgger data collection.

\begin{lstlisting}[style=ccode, label=lst:admm, caption={Inner loop of the C ADMM solver. Comments mark the algorithmic correspondence to (\ref{eq:admm_u}) -- (\ref{eq:admm_y}). All arrays are stack-allocated.}]
for (int k = 0; k < max_iters; ++k) {
    /* (5): u-update via cached Riccati */
    matvec(K_inf, x, Kx, NX, NX);
    for (int i = 0; i < NU; ++i)
        u[i] = -Kx[i] - d_ctrl[i]
             + rho_over_sigma * (z[i] - y[i]);

    /* (6): z-update via box projection */
    for (int i = 0; i < NU; ++i) {
        double v = u[i] + y[i] / rho;
        z[i] = clamp(v, u_min[i], u_max[i]);
    }

    /* (7): dual update */
    for (int i = 0; i < NU; ++i)
        y[i] += rho * (u[i] - z[i]);

    /* termination */
    if (primal_res(u,z) < tol &&
        dual_res(z,z_prev) < tol) break;
}
\end{lstlisting}

\subsection{Tracking and Latency Results}
\label{sec:results_admm}

We evaluate the controller in MuJoCo on a figure-8 trajectory of amplitude $0.5$~m and period $4.0$~s, yielding a peak speed of $1.11$~m/s, at a $100$~Hz control rate over $\sim 10$~s of closed-loop tracking after a $2$~s warmup. The tuned ADMM configuration ($\rho=3$, max\_iter $=50$, \texttt{eps} $=10^{-3}$) achieves $3.42$~mm steady-state RMSE. The speed-optimized configuration ($\rho=0.3$, otherwise identical) trades accuracy for latency, achieving $4.48$~mm RMSE at $3.2~\mu$s median solve time via single-iteration warm-start convergence on the slowly-varying reference: when the previous-step solution is consistent with the new optimum's effective feasibility region, a single ADMM iteration is sufficient. Table~\ref{tab:latency} summarizes the distribution across configurations. The tuned config's $9.4~\mu$s median converges in $4$ iterations; the original default ($\rho=1$, max\_iter $=200$, \texttt{eps} $=10^{-4}$) uses $10$ iterations at $23.1~\mu$s yet reaches only $3.72$~mm RMSE --- slower \emph{and} slightly less accurate than the tuned configuration, since closed-loop error is dominated by linearization against the nonlinear MuJoCo simulator rather than solver tolerance, so the $\rho$ value matters more than the iteration budget.

\begin{table}[t]
\centering
\caption{C ADMM solver latency on a Crazyflie figure-8 (peak $1.11$~m/s, $4$~s period, $100$~Hz), measured on a single core of an Intel i9-14900HX laptop CPU. Median and 95th-percentile solve times reported over closed-loop tracking after warmup. The speed-opt configuration achieves single-iteration warm-start convergence; the tuned configuration is the speed-accuracy Pareto-optimal point.}
\label{tab:latency}
\begin{tabular}{lrrrr}
\toprule
\textbf{Config} & \textbf{Median} & \textbf{P95} & \textbf{Iters} & \textbf{RMSE} \\
\midrule
speed-opt ($\rho{=}0.3$) & $3.2~\mu$s & $6.3~\mu$s & $1$ & $4.48$~mm \\
tuned ($\rho{=}3$) & $9.4~\mu$s & $15.5~\mu$s & $4$ & $3.42$~mm \\
original ($\rho{=}1$) & $23.1~\mu$s & $58.5~\mu$s & $10$ & $3.72$~mm \\
\bottomrule
\end{tabular}
\end{table}

\section{Solver Benchmarks}

\subsection{OSQP Comparison}

We reformulate (\ref{eq:mpc}) in OSQP's sparse standard form ($332$ decision variables, $584$ constraints) and run the same figure-8 scenario at $100$~Hz with the same warm-starting strategy. The tuned OSQP configuration (\texttt{eps\_abs} $=$ \texttt{eps\_rel} $= 10^{-3}$, polish disabled, max\_iter $= 50$, scaling $= 10$) converges to $4.86$~mm tracking RMSE at a median solve time of $203.4~\mu$s --- $22\times$ slower than tuned C ADMM at slightly worse accuracy. The OSQP timing is dominated by the per-iteration cost of the sparse KKT factorization update, which our cached Riccati recursion avoids entirely. A hyperparameter sweep on a Xeon-class CPU across \texttt{eps} in $\{10^{-2}, 10^{-3}, 10^{-4}, 10^{-5}\}$, max\_iter in $\{25, 50, 100, 250, 500\}$, and scaling in $\{0, 5, 10, 25, 50\}$, holding polish off and warm-start on for real-time fairness, confirmed that OSQP is bounded below by its per-iteration cost ($\sim 14~\mu$s per ADMM step at $25$ iterations) regardless of hyperparameter choice. The same qualitative finding holds on our headline laptop CPU: tighter tolerances either failed to converge within iteration budgets or did not improve closed-loop RMSE. The per-iteration cost is the binding constraint, not the iteration count.

\textbf{Hardware sensitivity.}\label{sec:hwsens} Solver speedups are robust to CPU choice within the same architecture class. Cross-validation on a Xeon-class host CPU produced C ADMM at $16.6~\mu$s and OSQP at $352.0~\mu$s on the same closed-loop figure-8 task, preserving the $\sim 21\times$ relative speedup at slightly different absolute timings. Both solvers scale proportionally with single-thread CPU performance, so the relative speedup is the deployment-relevant figure of merit. Embedded deployment on Cortex-M class microcontrollers is expected to be $\sim 100$--$1000\times$ slower across all CPU solvers in proportion, preserving relative ratios; STM32 deployment remains future work and is the next target for the open-source release.

\subsection{ReLU-QP: A Different Operating Regime}
\label{sec:reluqp}

ReLU-QP~\cite{bishop2024reluqp} is a recent ADMM solver that unrolls each iteration as a fixed-architecture neural-network forward pass: the linear-system solve becomes a matrix multiply against a precomputed weight matrix, the box projection becomes a ReLU-equivalent clamp, and the dual update is a residual connection. The architecture is designed for GPU parallelism, with reported advantages emerging at batched solving (many independent QPs per kernel launch).

We benchmarked ReLU-QP via its PyTorch reference implementation on the same closed-loop figure-8 task using an NVIDIA L40S datacenter GPU at batch size $1$, float64 precision, with adaptive $\rho$ enabled and a maximum of $4000$ ADMM iterations. The solver converged reliably to a median tracking RMSE of $4.85$~mm in a median of $25$ iterations --- statistically indistinguishable from OSQP's $4.86$~mm, as expected since both are first-order methods reaching the same constrained-LQR optimum. The achievable accuracy floor at $\approx 4.85$~mm reflects linearization error against the nonlinear MuJoCo simulator, not solver suboptimality.

However, ReLU-QP's median solve time was $1.84$~ms --- $196\times$ slower than our C ADMM. The underlying GPU compute completes in single-digit microseconds for our $80$-variable condensed QP; the dominant cost at batch size $1$ is kernel launch overhead and CPU$\leftrightarrow$GPU memory transfer of the cost vector and solution. ReLU-QP additionally incurs a $223$~ms first-invocation overhead from JIT compilation, which would require ground-side warm-up before onboard deployment.

We do not view this as a defect of ReLU-QP. Onboard MPC for a single robot is a single-problem batch$\,{=}\,1$ regime, which is not where ReLU-QP is designed to win. Its native operating point is batch $\gg 1$: multi-agent fleet MPC, Monte-Carlo trajectory sampling, or differentiable solver contexts where the GPU executes many independent QPs simultaneously and amortizes the kernel launch cost. Within those regimes ReLU-QP would be the correct tool. The contribution of this section is the empirical characterization of where the regime boundary falls, not a competitive comparison.

\subsection{Summary}

\begin{table*}[t]
\centering
\caption{Solver comparison on Crazyflie linear MPC ($N=20$, $n_x=12$, $n_u=4$) closed-loop on figure-8 ($1.11$~m/s peak) and helix. All solvers converge to the same constrained-LQR optimum; residual RMSE differences ($\lesssim 1.7$~mm across the nine rows) reflect first-order tolerance settings and the dominant hover-linearization error against nonlinear simulation. CPU rows for figure-8 use a single core of an Intel i9-14900HX laptop; CPU rows for helix use a Xeon-class host CPU (proportional scaling preserves relative speedups; see Hardware sensitivity, \S\ref{sec:hwsens}). ReLU-QP runs on an NVIDIA L40S GPU at batch size $1$, outside its intended high-batch operating regime.}
\label{tab:solvers}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lllrrll}
\toprule
\textbf{Solver} & \textbf{Config} & \textbf{Traj} & \textbf{Median} & \textbf{RMSE} & \textbf{Hardware} & \textbf{Notes} \\
\midrule
C ADMM (ours) & speed-opt ($\rho{=}0.3$) & fig-8 & $3.2~\mu$s & $4.48$~mm & i9-14900HX & 1-iter warm-start \\
C ADMM (ours) & tuned ($\rho{=}3$)       & fig-8 & $9.4~\mu$s & $3.42$~mm & i9-14900HX & Pareto-optimal \\
C ADMM (ours) & original ($\rho{=}1$)    & fig-8 & $23.1~\mu$s & $3.72$~mm & i9-14900HX & default baseline \\
OSQP          & tuned                     & fig-8 & $203.4~\mu$s & $4.86$~mm & i9-14900HX & sparse Cholesky \\
OSQP          & default                   & fig-8 & $201.6~\mu$s & $4.86$~mm & i9-14900HX & floors at per-iter \\
ReLU-QP       & bs$=1$, fp64              & fig-8 & $1{,}841.7~\mu$s & $4.85$~mm & L40S GPU   & batch$=1$ regime \\
\midrule
C ADMM (ours) & tuned                     & helix & $12.5~\mu$s     & $3.79$~mm & Xeon host  & cross-platform \\
OSQP          & default                   & helix & $357.1~\mu$s    & $5.10$~mm & Xeon host  & cross-platform \\
ReLU-QP       & bs$=1$, fp64              & helix & $1{,}820.3~\mu$s & $5.09$~mm & L40S GPU   & batch$=1$ regime \\
\bottomrule
\end{tabular}
\end{table*}

\section{Distillation: From MPC to a Neural Policy}
\label{sec:dagger}

\subsection{Why Distill}

The C ADMM is fast, but deployment still requires the full dynamics model, the cached Riccati matrices, and a working solver. For embedded or batched-inference scenarios it is attractive to compress the entire pipeline into a feedforward network: the network has no dynamics dependency at deployment, generalizes across the model uncertainty seen at training time, and runs as a single matrix-multiply chain. We use DAgger~\cite{ross2011dagger} with DART~\cite{laskey2017dart} noise injection.

\subsection{Network Architecture}

The policy is a three-layer MLP: $24 \to 64 \to 64 \to 4$ with LayerNorm on the input and tanh on the output. The input is the state error plus the next four reference waypoints; the output is in the normalized $[-1, 1]$ range and is rescaled to $(T, \tau_x, \tau_y, \tau_z)$. Total parameters: $6{,}276$.

\subsection{DAgger with DART}

Behavior cloning fails on this problem: a network trained purely on MPC rollouts diverges at deployment because the rollout distribution does not cover off-policy states. DART injects training-time noise on the expert action, sampled from $\mathcal{N}(\bm{0}, \alpha \Sigma_\text{expert})$ with $\alpha$ adapted to keep average TV-distance from the on-policy distribution below a threshold. This produces a covering dataset on which behavior cloning succeeds (with $13.1$~mm tracking, vs. crashing). DAgger then iteratively refines the policy by querying the expert on the student's rollout states; we ran $5$ iterations with $1{,}500$ episodes per iteration.

\subsection{Distilled Policy Results}

The final policy tracks the figure-8 at $4.1$~mm RMSE, $\sim 20\%$ degradation from the MPC teacher. Inference is implemented as plain C with hand-written matrix multiplies and runs in $2.1~\mu$s on the same CPU --- $\sim 4.5\times$ faster than the tuned C ADMM solver, with no dynamics model, solver, or external dependency in the deployment binary. A summary is given in Table~\ref{tab:dagger}.

\begin{table}[t]
\centering
\caption{MPC vs distilled policy on figure-8.}
\label{tab:dagger}
\begin{tabular}{lrr}
\toprule
\textbf{Controller} & \textbf{RMSE} & \textbf{Latency} \\
\midrule
LQR baseline & $9.2$~mm & $\sim 30~\mu$s (NumPy) \\
C ADMM MPC (tuned) & $3.42$~mm & $9.4~\mu$s \\
BC alone & --- & crashes \\
BC + DART & $13.1$~mm & $2.1~\mu$s \\
DAgger + DART (final) & $4.1$~mm & $2.1~\mu$s \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Trade-Offs}

The distilled policy is faster and dependency-free, but it is approximate (no constraint guarantees) and uninterpretable (a $6$K-parameter black box). The MPC remains the right choice when constraint satisfaction must be certified or when the dynamics model is expected to be reasonably accurate. A complementary approach we did not implement is differentiable MPC~\cite{amos2018diffmpc}: rather than replacing the solver with a network, backpropagate through the solver to learn its parameters ($Q$, $R$, model). This preserves constraint satisfaction at deployment while still benefiting from data.

\section{Discussion and Limitations}

\textbf{Linearization regime.} Tracking results are reported in simulation at $1.11$~m/s, where the body remains within $\sim 15^\circ$ of hover. Beyond $3$~m/s linearization error becomes the dominant tracking error source and a switch to nonlinear MPC or differential-flatness feedforward (e.g., the INDI inner loop of~\cite{tal2021indi}) would be required.

\textbf{Hardware deployment.} All numbers in this paper are simulation-side. The C ADMM has been written to be portable to STM32F4-class microcontrollers but has not been flashed to a physical Crazyflie. The published TinyMPC~\cite{nguyen2024tinympc} runs at $500$~Hz on the same MCU class with similar problem size, providing strong evidence that the deployment is feasible.

\textbf{ReLU-QP regime characterization.} Our ReLU-QP measurements are limited to batch size $1$ on a single GPU class (L40S). The native operating regime of ReLU-QP --- batched parallel solving of many independent QPs --- is outside the scope of this paper but is the right comparison for multi-agent fleet MPC, Monte-Carlo planning, or differentiable solver contexts. A careful sweep of the batch-size axis (where ReLU-QP's per-solve cost amortizes across the kernel launch) and the problem-size axis (where the GPU compute eventually dominates the launch overhead) would precisely locate the regime boundary; we did not perform this sweep. The published ReLU-QP scaling experiments target $n_x \approx 30$--$45$ legged robotics MPC, which sits closer to the regime where ReLU-QP's per-iteration cost becomes competitive with general-purpose CPU solvers.

\textbf{Distilled policy generalization.} The DAgger student was trained at a fixed mass and disturbance level. We did not run domain randomization or sim-to-real, and we expect tracking to degrade under battery-depletion mass changes, propeller damage, or wind disturbance --- closing those gaps would require either training-time domain randomization or test-time adaptation, neither of which is in scope here.

\section{Related Work}

\textbf{Embedded MPC solvers.} OSQP~\cite{stellato2020osqp} is the canonical sparse first-order QP solver; HPIPM~\cite{frison2020hpipm} provides interior-point methods specialized for MPC. TinyMPC~\cite{nguyen2024tinympc}, the most direct antecedent for this work, demonstrated $500$~Hz MPC on a Crazyflie microcontroller using the same Riccati-caching trick.

\textbf{Quadrotor MPC.} Tal and Karaman~\cite{tal2021indi} reach $66$~mm RMSE at $13$~m/s on a custom $800$~g quadrotor using INDI plus differential-flatness snap tracking. The Crazyswarm Mellinger baseline reports $\sim 20$~mm at moderate speeds. Our $3.42$~mm number at $1.11$~m/s is competitive in the slow regime in simulation; on hardware, $3$--$5$~mm is the practical floor due to airframe flex and motor variability.

\textbf{Policy distillation for MPC.} The MPC-as-teacher idea predates DAgger and has been explored extensively in autonomous driving and locomotion; for quadrotors, Loquercio et al.~\cite{loquercio2021agile} use IL from privileged simulators, and Song and Scaramuzza~\cite{song2022policy} explicitly train policies in the loop with MPC on quadrotors. Our contribution here is not the technique but the latency number ($2.1~\mu$s) and the explicit trade-off table.

\section{Conclusion}

We have shown that a $400$-line, dependency-free C ADMM solver tuned to the Riccati structure of quadrotor MPC tracks a Crazyflie figure-8 at $3.42$~mm RMSE at $9.4~\mu$s median solve time, $22\times$ faster than tuned OSQP. A general-purpose GPU solver (ReLU-QP) targets a different operating regime --- batched parallel solving, not single-problem onboard latency --- and incurs $196\times$ higher per-solve cost at batch size $1$ on this small QP. The result is consistent with ReLU-QP's published design and identifies the regime boundary, not a competitive failure. Distillation via DAgger compresses the entire stack into a $6$K-parameter network at $2.1~\mu$s deployment latency, with $\sim 20\%$ tracking degradation but no dynamics-model dependency. The full pipeline targets the production deployment regime of small-quadrotor autonomy stacks at companies that ship aerial robots.

\bibliographystyle{IEEEtran}
\begin{thebibliography}{99}

\bibitem{stellato2020osqp}
B.~Stellato, G.~Banjac, P.~Goulart, A.~Bemporad, and S.~Boyd, ``OSQP: an operator splitting solver for quadratic programs,'' \emph{Mathematical Programming Computation}, vol.~12, no.~4, pp.~637--672, 2020.

\bibitem{nguyen2024tinympc}
A.~Nguyen, S.~Schoedel, A.~Alavilli, B.~Plancher, and Z.~Manchester, ``TinyMPC: Model-predictive control on resource-constrained microcontrollers,'' in \emph{IEEE Int. Conf. on Robotics and Automation (ICRA)}, 2024, Best Paper in Automation.

\bibitem{bishop2024reluqp}
A.~Bishop, J.~Brüdigam, and Z.~Manchester, ``ReLU-QP: A GPU-accelerated quadratic programming solver for model-predictive control,'' in \emph{IEEE Int. Conf. on Robotics and Automation (ICRA)}, 2024.

\bibitem{boyd2011admm}
S.~Boyd, N.~Parikh, E.~Chu, B.~Peleato, and J.~Eckstein, ``Distributed optimization and statistical learning via the alternating direction method of multipliers,'' \emph{Foundations and Trends in Machine Learning}, vol.~3, no.~1, pp.~1--122, 2011.

\bibitem{ross2011dagger}
S.~Ross, G.~Gordon, and D.~Bagnell, ``A reduction of imitation learning and structured prediction to no-regret online learning,'' in \emph{Int. Conf. on Artificial Intelligence and Statistics (AISTATS)}, 2011.

\bibitem{laskey2017dart}
M.~Laskey, J.~Lee, R.~Fox, A.~Dragan, and K.~Goldberg, ``DART: Noise injection for robust imitation learning,'' in \emph{Conf. on Robot Learning (CoRL)}, 2017.

\bibitem{amos2018diffmpc}
B.~Amos, I.~D.~J.~Rodriguez, J.~Sacks, B.~Boots, and J.~Z.~Kolter, ``Differentiable MPC for end-to-end planning and control,'' in \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2018.

\bibitem{tal2021indi}
E.~Tal and S.~Karaman, ``Accurate tracking of aggressive quadrotor trajectories using incremental nonlinear dynamic inversion and differential flatness,'' \emph{IEEE Trans. Control Systems Technology}, vol.~29, no.~3, pp.~1203--1218, 2021.

\bibitem{frison2020hpipm}
G.~Frison and M.~Diehl, ``HPIPM: A high-performance quadratic programming framework for model predictive control,'' in \emph{IFAC World Congress}, 2020.

\bibitem{loquercio2021agile}
A.~Loquercio, E.~Kaufmann, R.~Ranftl, M.~Müller, V.~Koltun, and D.~Scaramuzza, ``Learning high-speed flight in the wild,'' \emph{Science Robotics}, vol.~6, no.~59, 2021.

\bibitem{song2022policy}
Y.~Song and D.~Scaramuzza, ``Policy search for model predictive control with application to agile drone flight,'' \emph{IEEE Trans. Robotics}, vol.~38, no.~4, pp.~2114--2130, 2022.

\end{thebibliography}

\end{document}
